\Title

### 2021-01-26 manuscript/manuscript.tex
Update manuscript/manuscript.tex
Co-authored-by: Santiago Soler <santiago.r.soler@gmail.com>

We assessed the trade-offs in interpolation accuracy and computation time of
the gradient-boosted equivalent sources algorithm as a function of the two key
controlling factors: the window size and the window overlap.
The comparisons were performed against a regular least-squares solution
(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
(Fig.~\ref{fig:synthetic-layouts}c-d) .
To avoid biasing the results, we used the same locations of equivalent sources
for both the regular and gradient-boosted interpolations, namely
block-averaged-sources with a block size of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.

>>>>

We assessed the trade-offs in interpolation accuracy and computation time of
the gradient-boosted equivalent sources algorithm as a function of the two key
controlling factors: the window size and the amount of overlap between adjacent
windows.
The comparisons were performed against a regular least-squares solution
(Eq.~\ref{eq:least_squares_solution}) using the synthetic airborne data
(Fig.~\ref{fig:synthetic-layouts}c-d) .
To avoid biasing the results, we used the same locations of equivalent sources
for both the regular and gradient-boosted interpolations, namely
block-averaged-sources with a block size of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthSpacing}{\meter} and a
relative depth of
\SI{\BestAirborneBlockAveragedSourcesRelativeDepthDepth}{\meter}.
